Perturbing SU($n$)-symmetric interactions

### 2020-02-05 collective_sun/sun_perturbation.tex
renamed some variables

Having identified diagrammatic representations of the coefficients
$A_6,A_4,A_2$, we now need to simplify all diagrams to reduce their
computational complexity, as discussed in Section \ref{sec:diagrams}.
Eliminating all filled dots in regions that address only one tensor
yields:
\begin{align}
  A_6 = D_1 - D_2 + D_3 - D_4,
\end{align}
\begin{align}
  A_4 = D_2 - 2 D_3 + 3 D_4,
  &&
  A_2 = D_3 - 3 D_4
\end{align}
where
\begin{align}
  D_1 \equiv \f18 \diagram{triple_0_o6},
  &&
  D_2 \equiv \f32 \diagram{triple_01_o4}
  - 2 \diagram{triple_1_o3},
  &&
  D_4 \equiv \diagram{triple_0111}.
\end{align}
\begin{align}
  D_3 \equiv 3 \diagram{triple_011_o2}
  + \f34 \diagram{triple_02_o2}
  - 6 \diagram{triple_11_o}
  + 2 \diagram{triple_2}.
\end{align}
Defining, for each of $m\in\set{u,v,w}$,
\begin{align}
  \m m \equiv \sum_{p,q} m_{pq} \op{p}{q},
  &&
  \v{\m m} \equiv \sum_{p<q} m_{pq} \ket{\set{p,q}},
  &&
  \v m \equiv \sum_p m_p \ket{p},
  &&
  m_p \equiv \sum_q m_{pq},
  &&
  \col{m} \equiv \sum_{p<q} m_{pq},
\end{align}
we can expand
\begin{align}
  D_1 = \col{u}\,\col{v}\,\col{w},
  &&
  D_2 = \col{u}\,\v v\c\v w + \col{v}\,\v w\c\v u
  + \col{w}\,\v u\c\v v - 2 \sum_p u_p v_p w_p,
  &&
  D_4 = \tr\p{\m u \c \m v \c \m w},
\end{align}
\begin{multline}
  D_3 = \v u \c\m v\c\v w + \v v \c\m w\c\v u + \v w \c\m u\c\v v
  + \col{u}\,\v{\m v}\c\v{\m w} + \col{v}\,\v{\m w}\c\v{\m u}
  + \col{w}\,\v{\m u}\c\v{\m v} \\
  - 2 \sum_{p,q} \p{u_p v_{pq} w_{pq}
    + v_p w_{pq} u_{pq} + w_p u_{pq} v_{pq}}
  + 4 \sum_{p<q} u_{pq} v_{pq} w_{pq}.
\end{multline}
Finally, we can also write the product $\X$ in \eqref{eq:triple_multi}
in terms of the collective operator $\col{X} \equiv \sum_p X_p$:
\begin{align}
  \X \EQFS
  \tilde A_6 \col{X}^6 + \tilde A_4 \col{X}^4 + \tilde A_2 \col{X}^2,
  \label{eq:triple_col}
\end{align}
where we have neglected scalar terms without physical consequence, and
\begin{align}
  \tilde A_6 \equiv \f{A_6}{N!_6},
  &&
  \tilde A_4 \equiv \f{A_4}{N!_4} - 5\p{3N-8} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4}
  + \p{45N^2-210N+184} \f{A_6}{N!_6}.
\end{align}

>>>>

Having identified diagrammatic representations of the coefficients
$A_6,A_4,A_2$, we now need to simplify all diagrams to reduce their
computational complexity, as discussed in Section \ref{sec:diagrams}.
Eliminating all filled dots in regions that address only one tensor
yields:
\begin{align}
  A_6 = D_0 - D_1 + D_2 - D_3,
  &&
  A_4 = D_1 - 2 D_2 + 3 D_3,
  &&
  A_2 = D_2 - 3 D_3
\end{align}
where
\begin{align}
  D_0 \equiv \f18 \diagram{triple_0_o6},
  &&
  D_1 \equiv \f32 \diagram{triple_01_o4}
  - 2 \diagram{triple_1_o3},
  &&
  D_3 \equiv \diagram{triple_0111}.
\end{align}
\begin{align}
  D_2 \equiv 3 \diagram{triple_011_o2}
  + \f34 \diagram{triple_02_o2}
  - 6 \diagram{triple_11_o}
  + 2 \diagram{triple_2}.
\end{align}
Defining, for each of $m\in\set{u,v,w}$,
\begin{align}
  \m m \equiv \sum_{p,q} m_{pq} \op{p}{q},
  &&
  \v{\m m} \equiv \sum_{p<q} m_{pq} \ket{\set{p,q}},
  &&
  \v m \equiv \sum_p m_p \ket{p},
  &&
  m_p \equiv \sum_q m_{pq},
  &&
  \col{m} \equiv \sum_{p<q} m_{pq},
\end{align}
we can expand
\begin{align}
  D_0 = \col{u}\,\col{v}\,\col{w},
  &&
  D_1 = \col{u}\,\v v\c\v w + \col{v}\,\v w\c\v u
  + \col{w}\,\v u\c\v v - 2 \sum_p u_p v_p w_p,
  &&
  D_3 = \tr\p{\m u \c \m v \c \m w},
\end{align}
\begin{multline}
  D_2 = \v u \c\m v\c\v w + \v v \c\m w\c\v u + \v w \c\m u\c\v v
  + \col{u}\,\v{\m v}\c\v{\m w} + \col{v}\,\v{\m w}\c\v{\m u}
  + \col{w}\,\v{\m u}\c\v{\m v} \\
  - 2 \sum_{p,q} \p{u_p v_{pq} w_{pq}
    + v_p w_{pq} u_{pq} + w_p u_{pq} v_{pq}}
  + 4 \sum_{p<q} u_{pq} v_{pq} w_{pq}.
\end{multline}
Finally, we can also write the product $\X$ in \eqref{eq:triple_multi}
in terms of the collective operator $\col{X} \equiv \sum_p X_p$:
\begin{align}
  \X \EQFS
  \tilde A_6 \col{X}^6 + \tilde A_4 \col{X}^4 + \tilde A_2 \col{X}^2,
  \label{eq:triple_col}
\end{align}
where we have neglected scalar terms without physical consequence, and
\begin{align}
  \tilde A_6 \equiv \f{A_6}{N!_6},
  &&
  \tilde A_4 \equiv \f{A_4}{N!_4} - 5\p{3N-8} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4}
  + \p{45N^2-210N+184} \f{A_6}{N!_6}.
\end{align}
